Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-01 article.tex
Expan benchmarks

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 fib & clang & greedy & briggs & linear \\ [0.5ex] 
 \hline
 40 & 1.000000 & 1.438693 & 1.441270 & 0.73 \\ [1ex] 
 41 & 1.000000 & 1.441035 & 1.440626 & 0.73 \\ [1ex] 
 \hline
\end{tabular}
\end{center}

bench clang	benches/fib.ll 42 	min=5494929992 (1.000000)	avg=5545852373 (1.000000)	max=5669289413
bench greedy	benches/fib.ll 42 	min=7951933724 (1.447140)	avg=7969947833 (1.437101)	max=8004638438
bench briggs	benches/fib.ll 42 	min=7946186345 (1.446094)

>>>>

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 fib & clang & greedy & simple & linear \\ [0.5ex] 
 \hline
 40 & 1.000000 & 1.438693 & 1.441270 & 0.73 \\ [1ex] 
 41 & 1.000000 & 1.441035 & 1.440626 & 0.73 \\ [1ex] 
 42 & 	1.000000 & 1.447140 & 1.446094 & 0\\
 \hline
\end{tabular}
\end{center}
